---
title: "Join us"
---

Please sign up using this [**Google form**](https://forms.gle/8TFEigaaWoJPGXPe8) to receive updates on our activities and events. The form is only checked periodically, so please be patient if you do not receive a response immediately. 

If you'd like to to get in touch directly, email us at ecoforecast.africa at the gmail.com domain.

## A quick overview of membership (as of November 2025)

```{r echo=FALSE, fig.cap = "", fig.asp = 1/2, fig.align = 'center', warning = F, message = F, out.width="100%"}
library(ggplot2)
library(dplyr)
library(googlesheets4)
library(viridis)

gs4_auth(email = "jslingsby@gmail.com")

dat = read_sheet("https://docs.google.com/spreadsheets/d/18NHGbF6ItGMOvmCg8c7ut4k5R_fqlBDAYViTihhcXwc/edit?resourcekey#gid=1238861919")

dcontdf <- dat %>% group_by(Continent) %>% summarise(value = n())

ddf <- dat %>% group_by(Country) %>% summarise(value = n())

world <- map_data("world")

world %>%
  merge(ddf, by.x = "region", by.y = "Country", all.x = T) %>%
  arrange(group, order) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = value)) +
  geom_polygon(color = "white", linewidth = 0.2) +
  scale_fill_viridis("", na.value = "gray90") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
```

Africa `r dcontdf$value[which(dcontdf$Continent == "Africa")]` (`r dat %>% filter(Continent == "Africa") %>% select(Country) %>% unique() %>% nrow()` countries) | North America `r dcontdf$value[which(dcontdf$Continent == "North America")]` | Europe `r dcontdf$value[which(dcontdf$Continent == "Europe")]` | Asia `r dcontdf$value[which(dcontdf$Continent == "Asia")]` | Many from or working in Africa


```{r echo=FALSE, fig.cap = "", fig.width=6, fig.align = 'center', warning = F, message = F, out.width="125%"}

# Make summary data
cridata <- dat %>% group_by(Role) %>% summarize(count = n()) %>%na.omit()

# Shorten labels and add linebreaks
cridata <- cridata %>% mutate(label = recode(Role, 
                          "Decision maker (e.g. conservation practitioner, government official, etc)" = "Decision maker",
                          "Faculty (Lecturer, Prof, etc)" = "Faculty",
                          "Non-academic Researcher" = "Non-academic \n Researcher"))

# Compute percentages
cridata$fraction <- cridata$count / sum(cridata$count)

# Compute the cumulative percentages (top of each rectangle)
cridata$ymax <- cumsum(cridata$fraction)

# Compute the bottom of each rectangle
cridata$ymin <- c(0, head(cridata$ymax, n=-1))

# Compute label position
cridata$labelPosition <- (cridata$ymax + cridata$ymin) / 2

# Make the plot
ggplot(cridata, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=label)) +
  geom_rect() +
  geom_text(x=4.6, aes(y=labelPosition, label=label, color=label)) + # x here controls label position (inner / outer)
  scale_fill_brewer(palette="Set1", direction = 1) +
  scale_color_brewer(palette="Set1", direction = 1) +
  coord_polar(theta="y") +
  xlim(c(2, 4.5)) +
  theme_void() +
  theme(legend.position = "none")
```

